### 2022-06-20 article_v2/tex/nsiTheory.tex
article v2

\section{Non-Standard Interactions}\label{sec:nsiTheory}
We have no reason to believe that the Standard Model 
gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and 
oscillations forces us to amend it. 
Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
properties might undergo a similar spontaneous symmetry break at high energies, 
producing at lower energies the Standard Model that we know. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.
In this sense, the Standard Model might be considered 
an effective low energy theory, which is yields impressive results in some areas, but failing in others.

@@

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
we are restricted to weak interactions that conserve lepton flavor. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
the off-diagonal elements constitute new sources of flavor violation.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
possibility of additional interactions that can cause the flavor change. Moreover, since we have 6 NSI parameters, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles, making the individual angles more inter-dependent than the NSI parameters, since combinations of them must satisfy the constraints of the matrix elements.

@@

\subsection{DeepCore and PINGU Signals}
The effect of NSI on the DeepCore event count has been previously discussed in~\cite{smirnovNSI}, while the NSI effect 
in PINGU has been studied in~\cite{choubey2014, ohlsson2013}.
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have averaged out.

@@

For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
have cascade events for DeepCore and PINGU. If we simulate 
$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
in the $\Pme$ probability. This indicating that the NSI parameters are much more influential at these energies, and that we should be able to 
constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.

>>>>

\section{Non-Standard Interactions}\label{sec:nsiTheory}
We have no reason to believe that the Standard Model 
gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and 
oscillations forces us to amend it. 
Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
properties might undergo a similar spontaneous symmetry break at high energies, 
producing at lower energies the Standard Model that we know. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.
In this sense, the Standard Model might be considered 
an effective low energy theory, which is yields impressive results in some areas but fails in others.

@@

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
we are restricted to weak interactions that conserve lepton flavor. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
the off-diagonal elements constitute new sources of flavor violation.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
possibility of additional interactions that can cause the flavor change. Moreover, since we have six NSI parameters, and the PMNS
matrix is parametrized with only three parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles. This makes the individual angles more inter-dependent than the NSI parameters since combinations of them must satisfy the constraints of the matrix elements.

@@

\subsection{DeepCore and PINGU Signals}
The effect of NSI on the DeepCore event count has been previously discussed in~\cite{smirnovNSI}, while the NSI effect 
in PINGU has been studied in~\cite{choubey2014, ohlsson2013}.
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have averaged out.

@@

For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
have cascade events for DeepCore and PINGU. If we simulate 
$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
in the $\Pme$ probability. This indicates that the NSI parameters are much more influential at these energies, and that we should be able to 
constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.
